Statistics Project

### 2022-12-12 StatsProject_draft_Caro.Rmd
Add RShiny App Files

Goal: Estimate how SalesPrice of the house is related to the square footage of the living area of the house & if SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in. We are only interested at looking at houses in the NAmes, Edwards & BrkSide neighborhoods.

@@

@@

## Linear Model 
```{r}
fit1 <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = train_a1)
summary(fit1)
confint(fit1)

>>>>

## Restatement of the Problem 
Estimate how SalesPrice of the house is related to the square footage of the living area of the house & if SalesPrice (and its relationship to square footage) depends on which neighborhood the house is located in. We are only interested at looking at houses in the NAmes, Edwards & BrkSide neighborhoods.

@@

From an initial examination of the scatter plots and histograms,

@@

## Linear Model

From a visual inspection of the Cook's D and residual plot, we notice there are 3 outliers: 
```{r}
fit1 <- lm(log(SalePrice) ~ log(GrLivArea) + Neighborhood + GrLivArea*Neighborhood, data = train_a1)
summary(fit1)
confint(fit1)
